\chapter{A Background Study}

\section{Fall Prevention and Rehabilitation Today}
Physiotherapy is a science related to the medical field, and central to this subject is movement. The subject of physiotherapy can be described as examining, treating and preventive, and includes manual techniques, exercises and possible use of technical methods. This subject is performed by a physiotherapist. Physiotherapists are traditionally working in the municipalities, hospitals and at private institutions, and they are working with both individual treatment and treatment in groups.\\ \\
Elderly people consult physiotherapists in terms of rehabilitation after a fall, stroke or other injuries, or if they want to become physically stronger to easier manage the everyday life. Physiotherapists sets up customized training for each customer according to what kind of needs that have. A customer spends about 1-2 hours per week with the physiotherapists, which is far too little time to become stronger or recovered from injuries. Therefore, one see the need for customers to practice outside of these hours at the physiotherapists. Physiotherapists gives the elderly exercises that they can practice at home, but not everyone is motivated by this and many skip the weekly exercise that are scheduled for them. 

\section{Exercise Games}
Digital games where exercise and game play are brought together are called exergames. Technology for tracking body movement, like motion sensors and remote controls, require the players to move which stimulates exercise. The combination of movement, fun and social interaction provides exergaming great potential for new business opportunities for the entertainment, recreation and healthcare sectors \cite{gamingforhealth}. \\ \\
Today there exist numerous types of games and technologies, where Nintendo Wii, Dance Dance Revolution, Playstation Eye Toy and Xbox Kinect are some of the more familiar technologies. This genres of games has become very popular, and due to the growing interests one has seen it as relevant to study the use in regard of health and education. The technology these games provide can in an interesting way help provide health-related information to specified target groups \cite{gamingforhealth}. In the past years exergames research has increased dramatically, and indications show that it will continue to do so \cite{chamberlin2008exergames}. Some research done on exergaming shows tremendous promise in academic, social and physical progress of youth using exergames. The health sector is now more focused on prevention of illness in stead of treatment,  where this type of research can contribute to use of exergames in health care \cite{gamingforhealth}. Games like Wii Sports and Dance Dance Revolution were designed to encourage physical activity, but many currently available exergames were not designed for this purpose. The popularity of exergames and the increasing customer appeal will improve design principles and physical requirements \cite{chamberlin2008exergames}. 
\subsection{Dance Dance Revolution}
Dance, Dance Revolution (DDR) is a series of video games created by Konami Corporation’s Bemani music games division. DDR is a rhythmic dance simulation game and was first released as an arcade game in 1998. In few years it became very popular, and the game has had its appearance on several game console systems like Sony Playstation, Nintendo 64, Microsoft Xbox and Nintendo GameCube \cite{bogost2005rhetoric}. DDR uses a touch-sensitive dance pad with sensors to register movements, where one shall press the right sensors in proper time with electronic dance music. Arrows on-screen gives direction on how and when to move around. The DDR games have varying difficulty, requiring different levels of physical activity. GetUpMove.com is an information website about the use of PlayStation Dance Dance Revolution as a weight loss tool. This site was launched in 2004, and one of the highlighted stories was about a young woman who lost about 95 pounds by using DDR as an exercise tool. This and similar stories got widespread exposure, and consumers started to buy DDR solely for the purpose of exercise \cite{bogost2005rhetoric}. In 2003, 5 years after the first release, Konami announce that DDR has reached a total sale of 6,5 million units worldwide \cite{gamespot}. 8 years later, in 2011, the number of sold units had reached over 13 million, which is  about 1 million units sold every year since the first release in 1998 \cite{gaygamer}. 

\subsection{PlayStation EyeToy}
In the early 2000s the PlayStation 2 EyeToy was released by Sony Inc. It was the first in this category of games to introduce a device that could translate human motions into a controller input and allow players to physically interact with virtual objects using their own body and without being connected to wires. \cite{eyetoy}. Human body movements are translated real-time into the controller input by a USB camera  and can also map the player’s face onto in-game characters. Eye Toy is easy to set up and its applications offer a lot of different environment and can be played by one or more players \cite{eyetoyrehab}.

\subsection{PlayStation Move}
PlayStation 3 Move was released in September 2010. The PlayStation Move’s interface consists of the Move Eye, a RGB camera with directive microphones, and the Motion Controller, a wand with an illuminating sphere attached to it. The camera can detect the sphere and determine where the wand is, which allows the players to interact with the PlayStation 3 through motion and position. The sphere attached to the wand helps the camera to determine the distance from the wand to the camera and to track the controllers position in three dimensions. The wand is equipped with a three-axis accelerometer and a three-axis gyro sensor which are used to track rotation in overall motion and can also be used to detect if the wand is out of range (i.e. hidden behind the player back). It also consists of a geomagnetic sensor used to calibrate the wand’s orientation against the Earth’s magnetic field, which makes it possible to recognize the wand’s position accurately.  (hmmm... hvordan kan denne setningen skrives på en annen måte?) \cite{comparison}. Up to four wands are supported at one time, which makes it possible for four players to play together. The color of the sphere can be changed to any color and is usually used to show what player is active and to give visual feedback \cite{ppmove}. The SDK is not made public, so its difficult for a third-party to make original applications \cite{comparison}. 

\subsection{Nintendo Wii}
Nintendo Wii was released in 2006 as the first motion sensor game. Only one year and 20 million units sold later, it became the market leader of that times generation of consoles. It consists of a Wii remote, which is the primary controller and a secondary controller called Nunchuk. The Nunchuk is connected at the bottom of the Wii remote control \cite{hackingwii}. The Wii remote contains 12 buttons, a 3-axis accelerometer, a high-resolution highspeed IR camera, a speaker, a vibration motor, and wireless Bluetooth connectivity.
Each Wii remote has a IR camera sensor on its tip. The camera ship can track up to four simultaneous IR light with high resolution and high speed. The accelerometer within the remote control provides the Wi remote’s motion-sensing capability.The Wii remote has a total of 12 buttons and the buttons are arranged symmetric so that both hands can be utilized. A vibrator motor, LED lights and a small speaker are used for different kinds of user feedback, like varying light strength and sound-effects. The four LED lights are also used to indicate the different players ID. Communication is sent over the wireless Bluetooth connections, which enables up to four controllers to be connected at the same time.  The users of Nintendo Wii can make their own personal profile, called Mii, where the data of the player will be directly connected up on the remote used. To operate, the remote needs two AA batteries \cite{hackingwii} \cite{whatiswii}. By December 2010 over 75 million Wii consoles were sold.  To complete the original system with improved accuracy and response time, Nintendo made an enhanced version, Wii Motion Plus, which was released in November 2009 \cite{consoles}.There are several SDKs for Nintendo Wii open, which makes it possible for a third party to develop applications which utilize the controller \cite{comparison}. 

\subsection{Wii Balance Board}
The Wii Balance board is an add-on accessory for the Wii Fit, which is a video game created by Nintendo to work with the Wii platform. Just like the Wii Remote controller, the balance board can read your body movements and give them back on the screen as you are playing \cite{whatiswiifit}. The balance board contains multiple pressure sensors which track body movements. The board has a area of 551 mm {*} 316 mm. A third party can also build applications for the balance board using the SDK WiimoteLib \cite{comparison}. It has been shown that game-based balance programs like Wii Balance Board compared to traditional training is easier, more motivating and more enjoyable \cite{taylor2011activity}.

\subsection{Xbox 360 Kinect}
Microsoft Kinect was released in 2010 and became quickly extremely popular. Only 25 days after its release it had sold 2.5 million units and by January 2012 Xbox 360 had sold over 66 million consoles and more than 18 million Kinect motion sensors \cite{consoles},  \cite{kinectsold}. Microsoft Kinect is a flexible low-cost motion sensor device for the Xbox 360 game console  and for Windows PCs that can track human motion. It is a webcam-based add-on peripheral for the console, which enables the user to play and interact with the game without physically holding a sensor device. Instead the player can interact with the game console through a natural user interface using gestures and voice commands (\cite{kinect}, siste setning kanskje litt avskrift.. se på senere). The device gives full-body 3D motion capture capabilities and gesture recognition by help of a RGB camera and a depth sensor \cite{kinect}. One advantage with Kinect is that it has an interface that senses players various motions and it also senses other objects in the field, which makes a natural environment where the players can interact with virtual objects in the real world. \cite{comparison}. Another advantage  is that its possible for a third party to write application for Kinect. Kinect for Windows SDK was released in June 2011 and enables developers to build Kinect applications with C++, C\# or Visual Basic using Microsoft Visual Studio 2010 \cite{kinectwindows}.

\section{Using Exergames for Fall Prevention and Rehabilitation: A background Study}
Games are becoming popular as a tool for exercise and rehabilitation. There have been a lot of different studies done on how some of the previous described types of exergames can be used for this. Most of the studies have been done on adolescents, but there also exists some research done directly on elderly. In this section we will review some of the interesting findings we did.\\ \\
Taylor et al. \cite{taylor2011activity} did a study where they searched through already done studies to draw a picture on how games can be used for exercise and rehabilitation. They reviewed some of the interesting findings they did in their paper.  From the studies they reviewed they found a trend; the  Energy Expenditure (EE) while playing Wii was greater than when doing sedentary activities, but not greater than brisk walking. This suggests that playing Wii sports could not replace real sports activities. Playing DDR on the other hand, maximum heart rate and oxygen consumption were greater compared with Wii Tennis, suggesting that DDR can substitute physical activity.
In their research they also found a study on what attitudes people have against DDR to encourage exercise. 40 postmenstrual women, aged 45-75 years old were asked. The overall attitude were positive; The game was fun and it gave a potential to improve coordination. They also expressed a concern about a long learning process. It is also found that playing against a human gave greater arousal ratings and physiological responses to gaming than when playing against a computer, which benefit the enjoyment, suggesting that this can be beneficial for older people. 
From their study they can conclude that computer-based rehabilitation is not a new phenomenon and that one of the main reasons for this is that games have the ability to increase motivation and produce distraction from daily, boring and painful treatments.Wii is seen as an attractive game for rehabilitation, both at home or in institutions. Wii is actually already in use within the National Health Service in UK and is commonly used for the elderly and patients with pathologies. \cite{taylor2011activity} \\ \\
Another study they found was that non-disabled  elderly (70 +/- 5,7 years) was positive to the EyeToy; they enjoyed it and found it easy to use. For patients with stroke it appeared to be less suitable, which could be even worse if they had to hold on to a controller. This suggests that EyeToy is more suitable for patients with stroke than for example Wii.  (litt usikker om vi bør ta dette fra den orginal kilden eller ikke)
Even though these these type of games are initially meant as entertainment systems, there are a number of studies that have used the hardware and developed software to turn for example the Wii into a useful rehabilitation tool. The importance of these games are entertainment that motivates for actual sports. This is very important in for example rehabilitation. \cite{taylor2011activity} \\ \\
Staiano and Calvert write about how exergames are more and more used in the health sector. Gaming consoles are already integrated into equipments at gyms and health clubs. An example is Concept 2’s rowing machine. Here the people exercising are motivated through competition and through virtual trainers who monitor their progress and encouraging them to proceed to the next level. Also some schools are starting to integrate these games into their curriculum. In all of West Virginia’s 765 public schools they have integrated DDR in their physical education. This has proven to be very effective and popular and some students lost 5-10 pounds after playing DDR daily. \cite{staiano2011exergames}. \\ \\
Williams et al. did a study to see if exergames, more specifically Nintendo WiiFit, was an applicable type of exercise to reduce the falling statistics of community-dwelling people over 70 years. A group who attended WiiFit exercise sessions was compared with a group who went to a local falls group. 77 percent of the participants meant that if the exercise programme was more available people like themself would use it. 92 percent of the participants expressed that they wanted to exercise with the WiiFit in the future, while 61percent would choose to exercise with the WiiFit rather than attend a falls group. An improvement in Berg Balance Scale (BBS)\footnote{Berg Balance Scale (BBS), a performance based measure using 14 activities of daily living (range 0-56)\cite{excell}} at 4 weeks was seen in the group that played WiiFit, meaning that there is a potential to improve balance in this population. Despite this, there was no change in The Falls Efficacy Scale - International (FES-I)\footnote{The Falls Efficacy Scale - International (FES-I) (http://ageing.oxfordjournals.org/content/34/6/614.short)} at 4 weeks. The qualitative data for the group that played WiiFit showed improved confidence for the participants. The conclusion of the study is that WiiFit is acceptable in  older people with a history of falls and that it has the potential to improve balance and confidence. Further work has to be done to find and develop an acceptable exercise programme with the potential to improve balance in older individuals. \cite{excell}\\ \\
Chang et al. did a study where they prototyped a Kinect game that was designed to help motivate people with motor disabilities to do their exercise more frequently and to improve the motor proficiency and quality of life. Because of the inconvenience of having to wear sensors in some of the other relevant technologies, Chang et al. chose to use Kinect. They developed a game, called “Kinerehab”, that was meant to assist therapists in rehabilitating students in public school settings. To detect the students’ movements Kinerehab uses image processing technology of Kinect. To engage and motivate the student for physical rehabilitation, the system is made with an interactive interface that has both audio and video feedback. For making it easy for therapists to review the progress of each students quickly, the system also includes details of students rehabilitation conditions which is automatically recorded in the system. Two students, a 16 year old girl diagnosed with having acquired muscle atrophy and insufficient muscle endurance, and a 17 year old boy diagnosed with cerebral palsy, were chosen to participate in the study. The girl used a wheelchair and could only stand up with assistance. The study included two phases: a baseline phase  where no assistive technology was applied, and the intervention phase where the Kinerehab was used. Both phases were done twice, beginning with the baseline phase, continuing with the intervention phase and so on. In both phases the same exercises were done. The result showed that both participants increased the number of correct movements significantly in the intervention phase. On average the the correct movements was 49 in the first baseline phase (5 sessions), while 170 in the first intervention phase (11 sessions). Both students indicated that the game motivated them to do the exercises and that they wanted to continue using it. The therapists said it would increase their workload a lot. This suggests that Kinect can be a viable rehabilitation tool, but further work, where more people with disabilities participate, should be done. \cite{kinect}





