\chapter{Motivation}

\section{The Problem of Falls}
Falls are very common in the older population. Even though it does not necessarily seems like a very serious event, it is actually the leading cause of injury in older people.  Fall is actually considered a public health problem because of the serious consequences for the person falling and their considerable cost to the country. \cite{otago}
It is estimated that around 30 percent of people over 65 years old and almost 50 percent of people over 80 years old fall at least once a year. 1/10 of these falls results in fracture and one-fifth needs medical treatment. Other serious outcomes of a fall includes pain, trama and impaired function \cite{otago}.  The worse outcome of a fall is death. 25 percent of elderly getting hip fracture after a fall, dies within a year \cite{gruppetrening-trheim} \cite{larhalsbrudd}. It is shown that after a fall one-third will be afraid of falling again. Being afraid of falling make them insecure which can result in a even bigger risk of falling. For many elderly, the fair of falling can result in them being less active and a loss of confidence in carrying out everyday activities. This can result in fair of leaving their house, which can lead to total inactivity. The latter is a serious problem because a long time of inactivity will result in disabilities and increased risk of falling. Therefore it is important to find ways to activate the elderly and to offer a service that can prevent the elderly from developing disabilities \cite{gruppetrening-trheim}. Another issue is that missing the ability to carry out everyday activity can result in loneliness and even depression (site dette? ). Falls are also resulting in an increase in economic costs, including both the acute treatment after a fall and often also in long-term care. \cite{otago}\\ \\

\section{Excisting Prevention Programs}
To prevent developing disabilities elderly should regularly perform a training program that strengthen their muscles, improve balance and coordination, endurance and mobility \cite{gruppetrening-trheim}. These kind of training programs are offered in Trondheim. There has been established various fitness groups; do you want to get back in shape and become physically stronger? do you feel unsteady and see the need for better balance? Do you manage less now than you did a year ago? Do you find it difficult to go outside? These fitness groups find place at various locations around Trondheim and are offered 1-2 hours one day a week. In addition there exists senior dance, walking groups and water gymnastics \cite{trim}. These activities are good initiatives, but when the main problem for Olga is that she's afraid to go outside, how will she manage to engage in these fitness groups? It is also shown that 2 hours a week with physical activity is not nearly enough to increase Olga’s physical strength \cite{gruppetrening-trheim}. Regular physical activity is the key to become physically stronger and obtain better balance. \\ \\
Trondheim municipality did a study where they provided a once a week group training program for elderly. Their study showed that training once a week did not improve physical function for the participants, but the participants expressed that they were less afraid of falling after starting with the group training. The study suggests that this kind of program should be combined with home training programs or other extra physical training offerings \cite{gruppetrening-trheim}. \\ \\
We found that there are already some offered training programs for elderly that can be implemented in their home:\\ \\
The \emph{“Otago”-program} is a program developed as a home training program for elderly to prevent falls. It consists of exercises that take about 30 minutes to complete which should be performed three times a week in addition to a walk twice a week. Each customer receives a booklet with instructions for the individual exercises prescribed in addition to ankle cuff weights. The participants needs to record the days they complete the program for follow-up purposes. For follow-up an instructor should do home visits every six months and telephone them every month. The instructor can then increase the difficulty in the prescribed exercises for each individual. The program has been tested and evaluated for 1016 home living people aged 65 to 97. The program was shown to reduce falls and falls related injuries with 35 percent, with the highest effect on those over 80 years old and those that have had a previous fall. The participants experienced improved strength and balance, as well as they maintained their confidence so it was easier for them to do everyday activities without being afraid of falling. \cite{otago} \cite{gruppetrening-trheim}\\ \\
\emph{Falls Management Exercise} (FaME) is an exercise program consisting of tailored group and home-based exercises and builds on the core exercises from the “Otago”-program.  There are a total of three group training sessions per week, in addition to two home-training sessions per week. The exercise intervention is designed to improve participants dynamic balance and core and leg strength.  In the United Kingdom a study was done where they examined the effectiveness of this program for home-living women aged 65 or older who had already fallen 3 or more times within the previous year. After using FaME for 36 weeks the fall rate was reduced by one-third. The conclusion of the study was that the exercise program should last for at least 36 weeks including at least 2 hours of training per week. For progression it is important that the intensity, resistance, and weight are continually increased, as well as the balance gets challange.\cite{fame}\\ \\
\emph{{Ø}velsesbanken} is a Scandinavian project providing a user profile with different training programs. The different exercises are developed from the two previous described concepts and other relevant studies on balance and exercising for elderly. The program gives an idea on how you can put together an exercise program customized for each individual. It is primarily made as a tool for physiotherapists for putting together training programs for their patients to do at home. As we see it, it can also be used as a tool for each individual to put together their own program, because you can also log in as a private user and make your own program. The program offers the user a choice of different exercises that you can add to your exercise program. When all exercises are chosen you can print out pdf-files with pictures and descriptions or you can read from the computer screen. It is an easy, self-explanatory and straightforward program to use. {Ø}velsesbanken is in use in Scandinavia and the summer of 2012 it had reached 4300 users. \cite{ovelsesbank}\\ \\

\section{Exergames used as a Exercise tool}
The new generation of video games that combine game play and physical activity is called exergames, and it has shown promise in effecting users health in a positive direction \cite{promotingexercise}. Exergames has proved to be motivating because of its easy understanding, accessibility and fun. This type of games are suitable for people in various age groups because most of the games does not require any prior knowledge of either computers or video games \cite{garcia2012exergames}. Use of exergames is also an important factor to the social aspect, because of the possibility of playing with others, something that will be entertaining for elderly who are often alone and experience loneliness as a part of the everyday life \cite{exergamesforelderly}. It has also been shown that this type of exercise improves moods \cite{staiano2011exergames}. The feeling of accomplishment users get from reaching goals, completing exercises and being in physical activity increases the users mood. This combined with the social interaction you get from playing provides a desire to play again \cite{exergamesforelderly} \cite{staiano2011exergames}. Exergames has shown promise in rehabilitation of balance after stroke and damage to the spine. The use of exergame also has an appropriate use in exercise and rehabilitation, because the fun and challenges you get through the game could take the focus away from boredom and any physical pain \cite{exergamesforelderly} \cite{lange2011development}. Today there exist numerous games of this type, but very few commercial games are suitable for the focused, controlled exercise required for therapy \cite{lange2011development}. The existing games are unfortunately too complicated, too rapidly and too difficult to handle for the elderly, and they have too complex and cumbersome consoles \cite{exergamesforelderly}. 

\section{Example Case}
78 year old Olga lives in her own apartment in central Trondheim. Everything she might need is situated in the area, but lately she has started  to feel unsteady and has trouble keeping her balance, making sure she does not go out more than necessary. Trondheim is also very icy most of the winter, which increases Olga's fear for falling. Basically, Olga is a very social person, but there has been little contact with friends and acquaintances lately because of the fear of going out. Olga has no close family nearby. Beside the unsteadiness, Olga is very ambulatory without any physical pain, and thus has no need for physiotherapists. Olga has a great desire to be more steady on her feet so that she can gain an increased social contact, and particularly increase her confidence. \\ \\
Olga has a grandson who is very into video games. Once a year he is visiting his grandmother. Every time he is visiting he tells her about the different games he is playing, and sometimes he also bring them to her house. One time he tells her about a new game he got for his birthday, a game where he did not need any controllers, but could only stand in front o the TV screen making moves that would appear on the screen.Olga thinks this sounds very interesting, but at the same time it sounds too intimidating so she would never buy anything like this herself. \\ \\
Two months later, Olga feels that she has become weaker after being inactive for so long. Her daughter recommends her visiting a physiotherapist. The clinic is only a couple blocks away from her house, but everyday before her appointment she thinks about how she will get there. She is very anxious about this, and ends up ordering a taxi. \\ \\
The physiotherapist, a young man, meets her in the door, and follows her into his office. After being examined the physiotherapist introduces her to a new project they have just started at his clinic. He tells about an exercise program as a video game that is specially made for elderly people. At first it will just be provided at the clinic, but eventually they have plan to offer it for patients to rent or buy. Olga think this sounds familiar and suddenly she remembers her grandson and the video games he was telling her about. She really wants to sign up for this program, but has one concern. How will she get to the clinic? The physiotherapist tells her that as part of the program, they will offer the participants transportations the three first times. But after that they will have to get there on their own. The reasons for this is because the main reason for the game is to strengthen their muscles and improve their balance, so after some time, they should feel more confident carrying out everyday activities. 

