\chapter{Conclusion}
There is great uncertainty related to the potential of this game. It is a new technological tool which will face a small and immature market. In addition, the fact that the game is not yet developed made it hard for us to understand the game, as well as describe the game to the physiotherapists that we interviewed. It was also difficult to predict a realistic demand. However, from the physiotherapists' positive attitude, and with support in the Norwegian health sector's new focus, we believe that the game has a potential in this market. The great amount of research that has been done on video games for health-related purposes the last couple of years, also suggest potential for the exergame. This requires Cyberlab to develop an entertaining and easy-to use game, customized with the right exercises for elderly, in close collaboration with the end-user and physiotherapists. If they do this, they can expect to become successful in this market and gain significant profit.  
\section{Future Work}
Future work for Cyberlab will be to find out how their exergame should be made. They know which exercises that are good for the end-user, but they have to find a way to integrate them into an entertaining and motivating concept, that can be customized for the users' needs and interests.  This should be done in a way that makes the game easy to use. As a part of this, it needs to be done more research on what type of games that are suitable for elderly.  In the making of the exergame, they should consider to offer the opportunity to multi-play, as this would most likely be much appreciated by both the physiotherapists and the end-user. \\ \\
The infrastructure of the game has to be well thought through. They have to find out where data will be stored, and how the data can be transferred from entity to entity. This includes the security aspects of having private information stored on a server. Cyberlab should also take the ethical aspects of storing and processing personal data into account. \\ \\
Finally, we will suggest to look into what kind of business potential the game has with other customer segments. This includes customer segments discussed in Chapter 9. In particular the potential of this game throughout Europe should be analysed, since the development of this game is part of an EU-funded project. The market potential will increase tremendously if they expanded to the rest of Europe. This requires new business models. \\ \\