
\documentclass[b5paper,twoside,openright,11pt]{report}
\usepackage[printonlyused]{acronym}
\usepackage{graphicx}
\usepackage{cite}
\usepackage[utf8]{inputenc}
\usepackage[hyphens]{url}

\pagenumbering{gobble}
\begin{document}
\chapter*{Problem Description} 
Games are becoming more and more important in the health sector. One specific genre of games is exercise games (exergames). In this assignment we will focus on the business opportunities and economics of games in the health sector, with special focus on exergames for rehabilitation and elderly. The work has been done in collaboration with Cyberlab, a company focusing on serious games for education and training. The work will provide background information and input to an EU funded project focusing on elderly afraid of falling.

In particular, the following studies will be done: 
\begin{itemize}
\renewcommand{\labelitemi}{$\bullet$}
\item A background study of exergames in general and exergames for rehabilitation and elderly in particular.
\item	A description of specific business cases.
\item	Analyzing the business potential of this type of games in the health sector using Osterwalder business model.
\item	Miscellaneous aspects to consider about this type of game
\end{itemize}
\cleardoublepage
\chapter*{Abstract}
\cleardoublepage
\chapter*{Preface}
\cleardoublepage
\pagenumbering{roman}
\tableofcontents
\cleardoublepage
\input{acronyms}
\cleardoublepage
\listoffigures
\cleardoublepage
\listoftables
\cleardoublepage
\pagenumbering{arabic}
\input{introduction}
\cleardoublepage
\input{motivation}
\cleardoublepage
\input{healthpolitics}
\cleardoublepage
\input{technological}
\cleardoublepage
\input{osterwalderbusinessmodel}
\cleardoublepage
\input{discussionInterview}
\cleardoublepage
\input{business-model-of-case}
\cleardoublepage
\input{discussion}
\cleardoublepage
\input{conclusion}
\cleardoublepage
\bibliography{bib}
\bibliographystyle{unsrt}
\addcontentsline{toc}{chapter}{Bibliography}
\pagenumbering{gobble}
\addcontentsline{toc}{chapter}{Appendix}
\cleardoublepage
\input{appendix}
\end{document}